Quantitative Benchmarking for Automatically Generated Conjectures

### 2018-03-12 TEBenchmarkPaper/article.tex
IsaCoSy interpretation

The most striking result is how rapidly IsaCoSy's running time increases with
sample size: from size 7 upwards, all runs failed (most timed out, a few aborted
early due to running out of memory). As we found with our preliminary testing,
this increase appears exponential, so even large increases to the timeout would
not produce many more successes.

>>>>

The most striking result is how rapidly IsaCoSy's running time increases with
sample size: from size 7 upwards, all runs failed (most timed out, a few aborted
early due to running out of memory). As we found with our preliminary testing,
this increase appears exponential, so even large increases to the timeout would
not produce many more successful observations. A significant amount of IsaCoSy's
time (around 50 seconds) was spent loading the generated theory (containing all
distinct datatypes and functions from TIP); this overhead is unfortunate, but
since it is constant across all sample sizes it does not affect our conclusions.

With so few successful datapoints it is difficult to make strong claims about
the precision/recall quality of IsaCoSy's output. It is clear from the quantity
of non-zero proportions that IsaCoSy is capable of discovering interesting
conjectures, and the graphs appear to follow the same shapes as those of
QuickSpec (decreasing precision, flat recall), although the error margins are
too wide to be definitive.
